Making Sequential Programs Deterministic

### 2019-03-23 design.tex
more text

\subsection{Discussion on defaulting rules}\label{defaulting}

\begin{itemize}
    \item All method parameters and return types (including constructors) are \<@PolyDet>.
    \item Reason: We want to be able to report nondeterministic behavior only where it is invalid.
    \item Example of a method with params and return types annotated as \<@PolyDet>.
    This method called from 2 places - one harmless(@Det instantiations), and another that call with \<@NonDet> args and prints the retun type.
    \item Exception to this defaulting is the construction of HashSets and HashMaps because they can't be \<@Det>.
    We explicitly annotate the return type on constructors as
        \<@OrderNonDet> and disallow constructing \<@Det HashSet> or \<@Det
        HashMap>.
\end{itemize}

>>>>

\subsection{Discussion on defaulting rules}\label{defaulting}
In our determinism checker, we chose \<@PolyDet> as the default for all method parameters and return types including constructors.
The rationale for this design choice was to not make our type checker too restrictive by making everything \<@Det>.  This implies that
the checker still allows some non-determinism as long as it doesn't break any determinism specifications explicitly written by the programmer.

\begin{itemize}
    \item Example of a method with params and return types annotated as \<@PolyDet>.
    This method called from 2 places - one harmless(@NonDet instantiations but no printing), and another that call with \<@NonDet> args and prints the return type.
    \item Exception to this defaulting is the construction of HashSets and HashMaps because they can't be \<@Det>.
    We explicitly annotate the return type on constructors as
        \<@OrderNonDet> and disallow constructing \<@Det HashSet> or \<@Det
        HashMap>.
\end{itemize}
